% add \usepackage{seqsplit} to your preamble 
\seqsplit{om:Temperature~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{OntoClimateAdapt:AgeSpecificPopulationDensity~{$\sqsubseteq$}~OntoClimateAdapt:PopulationDensity} \\
\seqsplit{OntoClimateAdapt:AnnualFrequency~{$\sqsubseteq$}~OntoClimateAdapt:TemporalFrequency} \\
\seqsplit{OntoClimateAdapt:ClimateAdaptationAction~{$\sqsubseteq$}~OntoClimateAdapt:AdaptationMeasure} \\
\seqsplit{OntoClimateAdapt:ClimateChange~{$\sqsubseteq$}~OntoClimateAdapt:EarthSystemPhenomenon} \\
\seqsplit{OntoClimateAdapt:ClimateChange~{$\sqsubseteq$}~OntoClimateAdapt:EnvironmentalPhenomenon} \\
\seqsplit{OntoClimateAdapt:Heatwave~{$\sqsubseteq$}~OntoClimateAdapt:MeteorologicalExtremeEvent} \\
\seqsplit{OntoClimateAdapt:InfrastructureResilienceMeasure~{$\sqsubseteq$}~OntoClimateAdapt:AdaptationMeasure} \\
\seqsplit{OntoClimateAdapt:MonthlyFrequency~{$\sqsubseteq$}~OntoClimateAdapt:TemporalFrequency} \\
\seqsplit{OntoClimateAdapt:NumberOfHeatwaveDays~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{OntoClimateAdapt:PolicyIntervention~{$\sqsubseteq$}~OntoClimateAdapt:AdaptationMeasure} \\
\seqsplit{OntoClimateAdapt:WeeklyFrequency~{$\sqsubseteq$}~OntoClimateAdapt:TemporalFrequency} \\
\seqsplit{{$\exists$}~om:hasUnit.{$\top$}~{$\sqsubseteq$}~om:Measure} \\
\seqsplit{{$\exists$}~om:hasValue.{$\top$}~{$\sqsubseteq$}~om:Quantity} \\
\seqsplit{{$\exists$}~time:hasBeginning.{$\top$}~{$\sqsubseteq$}~time:TemporalEntity} \\
\seqsplit{{$\exists$}~time:hasEnd.{$\top$}~{$\sqsubseteq$}~time:TemporalEntity} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:adaptedThrough.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:ClimateChange} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:affects.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:ClimateChange} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:forAgeGroup.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:AgeSpecificPopulationDensity} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasCause.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:ClimateChange} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasEffect.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:ClimateChange} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasFrequency.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:NumberOfHeatwaveDays} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasNumberOfHeatwaveDays.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:Location} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasPopulationDensity.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:Location} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasTemperature.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:Location} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasTimeInterval.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:NumberOfHeatwaveDays} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:isDerivedFromEvent.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:NumberOfHeatwaveDays} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:measuredBy.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:ClimateChange} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:occursAt.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:MeteorologicalExtremeEvent} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:studiedBy.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:ClimateChange} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~om:hasUnit.om:Unit} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~om:hasValue.om:Measure} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~time:hasBeginning.time:Instant} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~time:hasEnd.time:Instant} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:adaptedThrough.OntoClimateAdapt:AdaptationMeasure} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:affects.(OntoClimateAdapt:Ecology~{$\sqcup$}~OntoClimateAdapt:Economy~{$\sqcup$}~OntoClimateAdapt:HumanHealth)} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:forAgeGroup.OntoClimateAdapt:AgeGroup} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasCause.OntoClimateAdapt:GreenhouseGasEmission} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasEffect.(OntoClimateAdapt:MeteorologicalExtremeEvent~{$\sqcup$}~OntoClimateAdapt:OceanAcidification~{$\sqcup$}~OntoClimateAdapt:SeaLevelRise)} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasFrequency.OntoClimateAdapt:TemporalFrequency} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasNumberOfHeatwaveDays.OntoClimateAdapt:NumberOfHeatwaveDays} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasPopulationDensity.OntoClimateAdapt:PopulationDensity} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasTemperature.om:Temperature} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasTimeInterval.time:TemporalEntity} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:isDerivedFromEvent.OntoClimateAdapt:Heatwave} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:measuredBy.(OntoClimateAdapt:ClimateModel~{$\sqcup$}~OntoClimateAdapt:MeteorologicalStation~{$\sqcup$}~OntoClimateAdapt:SatelliteObservation)} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:occursAt.OntoClimateAdapt:Location} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:studiedBy.(OntoClimateAdapt:AtmosphericScience~{$\sqcup$}~OntoClimateAdapt:EnvironmentalScience~{$\sqcup$}~OntoClimateAdapt:Paleoclimatology)} \\
\seqsplit{{$\exists$}~om:hasNumericalValue.{$\top$}~{$\sqsubseteq$}~om:Measure} \\
\seqsplit{{$\exists$}~om:symbol.{$\top$}~{$\sqsubseteq$}~om:Unit} \\
\seqsplit{{$\exists$}~time:inXSDDate.{$\top$}~{$\sqsubseteq$}~time:Instant} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasMaximumAge.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:AgeGroup} \\
\seqsplit{{$\exists$}~OntoClimateAdapt:hasMinimumAge.{$\top$}~{$\sqsubseteq$}~OntoClimateAdapt:AgeGroup} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~om:hasNumericalValue.xsd:double} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~om:symbol.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~time:inXSDDate.xsd:string} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasMaximumAge.xsd:integer} \\
\seqsplit{{$\top$}~{$\sqsubseteq$}~{$\forall$}~OntoClimateAdapt:hasMinimumAge.xsd:integer} \\
